\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-07-12 write_up/mixfishsim_ecolmod.tex
Move discussion around

Our results demonstrate the importance of considering data scale and resolution
when using observational data to support management measures. We find that
understanding of the community composition dynamics will depend on the level of
data aggregation and that its important to consider the scale of process;
including population movement movement rates, habitat uniformity and fishing
targeting practices if potential biases in data are to be understood and taken
into account. Two contrasting real world approaches in this respect were the
spatial closures to protect cod in the North Sea. In one example, large scale
spatial closures were implemented with little success due to effort
displacement to previously unfished areas \citep{Dinmore2003}, while in another
small scale targeted spatiotemporal closures were considered to have some
effect in reducing cod mortality without having to disrupt other fisheries
significantly \citep{Needle2011}. These examples emphasise the importance of
considering the right scale and aggregation of data when identifying area
closures and the need to consider changing dynamics in the fisheries in
response to such closures. \\

%% key findings in context
\subsection{How does data aggregation and source impact on spatial fisheries
	management measures?}

From our simulations spatial disaggregation was more important than the
temporal disaggregation of the commercial data. This reflects the fact that
there was greater spatial heterogeneity over the spatial domain than
experienced in individual locations over the course of the year. This indicates
that fixed closures, if in the right locations, when based on commercially
derived data have the potential to reduced fishing mortality. The likely cost
of poor spatial and temporal resolution is associated with reduced
effectiveness and potentially closing fishing opportunities for other
fisheries. Our study showed that fishing rates on other populations also
changed (both up and down) as a side-effect of closures to protect one species.
This indicates the importance in considering fishing effort reallocation
following spatial closures, and our simulation allows us to consider the
spatiotemporal reasons for these changes.

>>>>

Our results demonstrate the importance of considering data scale and resolution
when using observational data to support management measures. We find that
understanding of the community composition dynamics will depend on the level of
data aggregation and its important to consider the scale of processes;
including population movement rates, habitat uniformity and fishing targeting
practices if potential biases in data are to be understood and taken into
account. 
%% key findings in context
\subsection{How does data aggregation and source impact on spatial fisheries
	management measures?}

From our simulations spatial disaggregation was more important than the
temporal disaggregation of the commercial data. This reflects the fact that
there was greater spatial heterogeneity over the spatial domain than
experienced in individual locations over the course of the year (Figure
\ref{S-fig:9}). This indicates that fixed closures, at the right resolution,
when based on commercially derived data have the potential to reduced fishing
mortality. The likely cost of poor spatial and temporal resolution is
associated with reduced effectiveness and potentially closing fishing
opportunities for other fisheries. \\

Two contrasting real world approaches in this respect were the spatial closures
to protect cod in the North Sea. In one example, large scale spatial closures
were implemented with little success due to effort displacement to previously
unfished areas \citep{Dinmore2003}, while in another small scale targeted
spatiotemporal closures were considered to have some effect in reducing cod
mortality without having to disrupt other fisheries significantly
\citep{Needle2011}. These examples emphasise the importance of considering the
right scale and aggregation of data when identifying area closures and the need
to consider changing dynamics in the fisheries in response to such closures. \\

Our study showed that fishing rates on other populations also changed (both up
and down) as a side-effect of closures to protect one species.  This indicates
the importance in considering fishing effort reallocation following spatial
closures, and our simulation allows us to consider the spatiotemporal reasons
for these changes.
